---
title: "R Notebook"
output: html_notebook
---

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# PREAMBLE 
# This section loads the required packages for this notebook. 
# All the required packages are already installed in the container

library(tidyverse)
library(magrittr)
library(glue)

```

# Introduction

This *R Markdown* notebook contains all the code for peforming the meta-analysis and generating the figures and tables. Each of the chunks below prepares the data for one of the models

```{r}
library(Matrix)
require(reshape2)
matrixlist.to.matrix <- function(matrixlist){
	G <- length(matrixlist)
	M <- bdiag(matrixlist[[1]])
	for(g in 2:G){ M <- bdiag(M,matrixlist[[g]]) }
	M <- as.matrix(M)
	M
}

dat <- read_csv("AllFischerData.csv")

```

## Meta-analysis

### Model 1

```{r}
# Prepare data for Model 1
tmp1 <- by(dat[,c("d250","d500","d750","d1000")], dat$Lab, colMeans)
tmp2 <- by(dat[,c("d250","d500","d750","d1000")], dat$Lab, function(x){apply(x,2,var)})
nn <- table(dat$Lab)
dat1 <- melt(sapply(tmp1, function(x){x}))
dat1$v <- melt(sapply(tmp2, function(x){x}))$value / nn[dat1$Var2]
dat1 <- data.frame(ConditionDescription="Not.Applicable", dat1)
colnames(dat1)[-1] <- c("DependentVariable", "LabID", "y", "v")
write.csv(dat1, file="model1.dat1.csv", row.names=FALSE, quote=FALSE)

## Added by Lincoln

write.csv(merge(as.data.frame(nn) %>% rename(LabID = Var1),dat1), 
          file = "model1.meta.csv", row.names = FALSE, quote = FALSE)

## ----------------




ulab <- unique(dat1$Lab)
vcv.list <- list(NULL)
for(i in 1:length(ulab)){
	sel <- dat$Lab==ulab[i]
	tmp.vcv <- cov(dat[sel,c("d250","d500","d750","d1000")])
	vcv.list[[i]] <- tmp.vcv / nn[ulab[i]]
}
dat2 <- matrixlist.to.matrix(vcv.list)
max(abs(dat1$v - diag(dat2)))
min(eigen(dat2)$values)	 >  1E-04
write.csv(dat2, file="model1.dat2.csv", row.names=FALSE, quote=FALSE)
# Analyze via: https://blakemcshane.shinyapps.io/mlmvmeta/
cat("Go to https://blakemcshane.shinyapps.io/mlmvmeta/\n")
cat("upload the files:\n")
cat("model1.dat1.csv\n")
cat("model1.dat2.csv\n")
cat("save the output as results1.Rdata\n\n")
```

### Model 2
```{r}
# Prepare data for Model 2
sel <- dat$FingerGroup %in% c("LS", "RS")
datFC <- dat[sel,]
datFC$FingerGroup <- factor(datFC$FingerGroup)
tmp1 <- by(datFC[,c("d250","d500","d750","d1000")], list(datFC$FingerGroup,datFC$Lab), colMeans)
tmp2 <- by(datFC[,c("d250","d500","d750","d1000")], list(datFC$FingerGroup,datFC$Lab), function(x){apply(x,2,var)})
tmp3 <- length(tmp1[[1]]) * length(dimnames(tmp1)[[1]])
nn <- table(datFC$FingerGroup,datFC$Lab)
dat1 <- melt(sapply(tmp1, function(x){x}))
dat1$v <- melt(sapply(tmp2, function(x){x}))$value / rep(as.vector(nn),each=length(tmp1[[1]]))
dat1 <- data.frame(ConditionDescription=rep(dimnames(tmp1)[[1]],each=length(tmp1[[1]])), 
					DependentVariable=dat1$Var1,
					LabID=rep(dimnames(tmp1)[[2]],each=tmp3),
					ConditionID=dat1$Var2,
					y=dat1$value,
					v=dat1$v)
write.csv(dat1, file="model2.dat1.csv", row.names=FALSE, quote=FALSE)

## Added by Lincoln

write.csv(merge(as.data.frame(nn) %>% rename(ConditionDescription = Var1, LabID = Var2),dat1), 
          file = "model2.meta.csv", row.names = FALSE, quote = FALSE)

## ----------------


umod <- unique(dat1$ConditionDescription)
ulab <- unique(dat1$Lab)
vcv.list <- list(NULL)
cnt <- 1
for(i in 1:length(ulab)){
	for(j in 1:length(umod)){
		sel <- datFC$Lab==ulab[i] & datFC$FingerGroup==umod[j]
		tmp.vcv <- cov(datFC[sel,c("d250","d500","d750","d1000")])
		m <- min(eigen(tmp.vcv)$values)
		
		
		vcv.list[[cnt]] <- tmp.vcv / nn[umod[j],ulab[i]]
		cnt <- cnt + 1	
	}
}
dat2 <- matrixlist.to.matrix(vcv.list)
max(abs(dat1$v - diag(dat2)))
min(eigen(dat2)$values)	 >  1E-04
write.csv(dat2, file="model2.dat2.csv", row.names=FALSE, quote=FALSE)

cat("Go to https://blakemcshane.shinyapps.io/mlmvmeta/\n")
cat("upload the files:\n")
cat("model2.dat1.csv\n")
cat("model2.dat2.csv\n")
cat("save the output as results2.Rdata\n\n")
```

### Model 3
```{r}
# Prepare data for Model 3
tmp1 <- by(dat[,c("d250","d500","d750","d1000")], list(dat$ReadingDir,dat$Lab), colMeans)
tmp2 <- by(dat[,c("d250","d500","d750","d1000")], list(dat$ReadingDir,dat$Lab), function(x){apply(x,2,var)})
for(i in 1:length(tmp1)){ if(is.null(tmp1[[i]])){ tmp1[[i]] <- rep(NA,4) } }
for(i in 1:length(tmp2)){ if(is.null(tmp2[[i]])){ tmp2[[i]] <- rep(NA,4) } }
tmp3 <- length(tmp1[[1]]) * length(dimnames(tmp1)[[1]])
nn <- table(dat$ReadingDir,dat$Lab)
dat1 <- melt(sapply(tmp1, function(x){x}))
dat1$v <- melt(sapply(tmp2, function(x){x}))$value / rep(as.vector(nn),each=length(tmp1[[1]]))
dat1 <- data.frame(ConditionDescription=rep(dimnames(tmp1)[[1]],each=length(tmp1[[1]])), 
					DependentVariable=dat1$Var1,
					LabID=rep(dimnames(tmp1)[[2]],each=tmp3),
					ConditionID=dat1$Var2,
					y=dat1$value,
					v=dat1$v)
write.csv(dat1, file="model3.dat1.csv", row.names=FALSE, quote=FALSE)


umod <- unique(dat1$ConditionDescription)
ulab <- unique(dat1$Lab)
vcv.list <- vcv.list2 <- list(NULL)
cnt <- 1
for(i in 1:length(ulab)){
	for(j in 1:length(umod)){
		sel <- dat$Lab==ulab[i] & dat$ReadingDir==umod[j]
		tmp.vcv <- cov(dat[sel,c("d250","d500","d750","d1000")])
		vcv.list[[cnt]] <- tmp.vcv / nn[umod[j],ulab[i]]

		if(sum(sel)>1){ m <- min(eigen(tmp.vcv)$values)	}else{m <- -1}
		if(m < 1E-04 ){ 
			cat(umod[j], ", ", ulab[i], ", ", nn[umod[j],ulab[i]], ", ", m, "\n")
			tmp.vcv <- matrix(NA, nrow(tmp.vcv), ncol(tmp.vcv))
		}
		vcv.list2[[cnt]] <- tmp.vcv / nn[umod[j],ulab[i]]

		cnt <- cnt + 1	
	}
}
dat2 <- matrixlist.to.matrix(vcv.list)
max(abs(dat1$v - diag(dat2)))
max(abs(dat1$v - diag(dat2)), na.rm=TRUE)
# min(eigen(dat2)$values)	 >  1E-04
 write.csv(dat2, file="model3.dat2.csv", row.names=FALSE, quote=FALSE)


dat2 <- matrixlist.to.matrix(vcv.list2)
sel <- !is.na(diag(dat2))
max(abs(dat1$v[sel] - diag(dat2)[sel]))
min(eigen(dat2[sel,sel])$values)	 >  1E-04
write.csv(dat1[sel,], file="model3.dat1.csv", row.names=FALSE, quote=FALSE)
write.csv(dat2[sel,sel], file="model3.dat2.csv", row.names=FALSE, quote=FALSE)


## Added by Lincoln

write.csv(merge(as.data.frame(nn) %>% rename(ConditionDescription = Var1, LabID = Var2),dat1[sel,]), 
          file = "model3.meta.csv", row.names = FALSE, quote = FALSE)

## ----------------
cat("Go to https://blakemcshane.shinyapps.io/mlmvmeta/\n")
cat("upload the files:\n")
cat("model3.dat1.csv\n")
cat("model3.dat2.csv\n")
cat("save the output as results3.Rdata\n\n")
```


### Model 4

```{r}
# Prepare data for Model 4
tmp1 <- by(dat[,c("d250","d500","d750","d1000")], list(dat$Hand,dat$Lab), colMeans)
tmp2 <- by(dat[,c("d250","d500","d750","d1000")], list(dat$Hand,dat$Lab), function(x){apply(x,2,var)})
tmp3 <- length(tmp1[[1]]) * length(dimnames(tmp1)[[1]])
nn <- table(dat$Hand,dat$Lab)
dat1 <- melt(sapply(tmp1, function(x){x}))
dat1$v <- melt(sapply(tmp2, function(x){x}))$value / rep(as.vector(nn),each=length(tmp1[[1]]))
dat1 <- data.frame(ConditionDescription=rep(dimnames(tmp1)[[1]],each=length(tmp1[[1]])), 
					DependentVariable=dat1$Var1,
					LabID=rep(dimnames(tmp1)[[2]],each=tmp3),
					ConditionID=dat1$Var2,
					y=dat1$value,
					v=dat1$v)
write.csv(dat1, file="model4.dat1.csv", row.names=FALSE, quote=FALSE)





umod <- unique(dat1$ConditionDescription)
ulab <- unique(dat1$Lab)
vcv.list <- vcv.list2 <- list(NULL)
cnt <- 1
for(i in 1:length(ulab)){
	for(j in 1:length(umod)){
		sel <- dat$Lab==ulab[i] & dat$Hand==umod[j]
		tmp.vcv <- cov(dat[sel,c("d250","d500","d750","d1000")])
		vcv.list[[cnt]] <- tmp.vcv / nn[umod[j],ulab[i]]

		m <- min(eigen(tmp.vcv)$values)	
		if(m < 1E-04 ){ 
			cat(umod[j], ", ", ulab[i], ", ", nn[umod[j],ulab[i]], ", ", m, "\n")
			tmp.vcv <- matrix(NA, nrow(tmp.vcv), ncol(tmp.vcv))
		}
		vcv.list2[[cnt]] <- tmp.vcv / nn[umod[j],ulab[i]]

		cnt <- cnt + 1	
	}
}
dat2 <- matrixlist.to.matrix(vcv.list)
max(abs(dat1$v - diag(dat2)))
min(eigen(dat2)$values)	 >  1E-04
write.csv(dat2, file="model4.dat2.csv", row.names=FALSE, quote=FALSE)


dat2 <- matrixlist.to.matrix(vcv.list2)
sel <- !is.na(diag(dat2))
max(abs(dat1$v[sel] - diag(dat2)[sel]))
min(eigen(dat2[sel,sel])$values)	 >  1E-04
write.csv(dat1[sel,], file="model4.dat1.csv", row.names=FALSE, quote=FALSE)
write.csv(dat2[sel,sel], file="model4.dat2.csv", row.names=FALSE, quote=FALSE)

cat("Go to https://blakemcshane.shinyapps.io/mlmvmeta/\n")
cat("upload the files:\n")
cat("model4.dat1.csv\n")
cat("model4.dat2.csv\n")
cat("save the output as results4.Rdata\n\n")
write.csv(merge(as.data.frame(nn) %>% rename(ConditionDescription = Var1, LabID = Var2),dat1[sel,]), 
          file = "model4.meta.csv", row.names = FALSE, quote = FALSE)

```


### Model 1 B: guess rejected particpants

```{r}
# Prepare data for Model 1 (guess rejected participants)
dat <- read.csv("RejectedFischerData.csv", header=TRUE)

tmp1 <- by(dat[,c("d250","d500","d750","d1000")], dat$Lab, colMeans)
tmp2 <- by(dat[,c("d250","d500","d750","d1000")], dat$Lab, function(x){apply(x,2,var)})
nn <- table(dat$Lab)
dat1 <- melt(sapply(tmp1, function(x){x}))
dat1$v <- melt(sapply(tmp2, function(x){x}))$value / nn[dat1$Var2]
dat1 <- data.frame(ConditionDescription="Not.Applicable", dat1)
colnames(dat1)[-1] <- c("DependentVariable", "LabID", "y", "v")
write.csv(dat1, file="model1b.dat1.csv", row.names=FALSE, quote=FALSE)

## Added by Lincoln

write.csv(merge(as.data.frame(nn) %>% rename(LabID = Var1),dat1), 
          file = "model1b.meta.csv", row.names = FALSE, quote = FALSE)

## ----------------




ulab <- unique(dat1$Lab)
vcv.list <- list(NULL)
for(i in 1:length(ulab)){
  sel <- dat$Lab==ulab[i]
  tmp.vcv <- cov(dat[sel,c("d250","d500","d750","d1000")])
  vcv.list[[i]] <- tmp.vcv / nn[ulab[i]]
}
dat2 <- matrixlist.to.matrix(vcv.list)
max(abs(dat1$v - diag(dat2)))
min(eigen(dat2)$values)	 >  1E-04
write.csv(dat2, file="model1b.dat2.csv", row.names=FALSE, quote=FALSE)
# Analyze via: https://blakemcshane.shinyapps.io/mlmvmeta/

cat("Go to https://blakemcshane.shinyapps.io/mlmvmeta/\n")
cat("upload the files:\n")
cat("model1b.dat1.csv\n")
cat("model1b.dat2.csv\n")
cat("save the output as results1b.Rdata\n\n")
```

### Model 1 C: Eye-movement contaminated trials
```{r}
# Prepare data for Model 1 (Eye movement contaminated trials)
dat <- read.csv("ContaminatedFischerData.csv", header=TRUE)

tmp1 <- by(dat[,c("d250","d500","d750","d1000")], dat$Lab, colMeans)
tmp2 <- by(dat[,c("d250","d500","d750","d1000")], dat$Lab, function(x){apply(x,2,var)})
nn <- table(dat$Lab)
dat1 <- melt(sapply(tmp1, function(x){x}))
dat1$v <- melt(sapply(tmp2, function(x){x}))$value / nn[dat1$Var2]
dat1 <- data.frame(ConditionDescription="Not.Applicable", dat1)
colnames(dat1)[-1] <- c("DependentVariable", "LabID", "y", "v")
write.csv(dat1, file="model1c.dat1.csv", row.names=FALSE, quote=FALSE)

## Added by Lincoln

write.csv(merge(as.data.frame(nn) %>% rename(LabID = Var1),dat1), 
          file = "model1c.meta.csv", row.names = FALSE, quote = FALSE)

## ----------------




ulab <- unique(dat1$Lab)
vcv.list <- list(NULL)
for(i in 1:length(ulab)){
  sel <- dat$Lab==ulab[i]
  tmp.vcv <- cov(dat[sel,c("d250","d500","d750","d1000")])
  vcv.list[[i]] <- tmp.vcv / nn[ulab[i]]
}
dat2 <- matrixlist.to.matrix(vcv.list)
max(abs(dat1$v - diag(dat2)))
min(eigen(dat2)$values)	 >  1E-04
write.csv(dat2, file="model1c.dat2.csv", row.names=FALSE, quote=FALSE)
# Analyze via: https://blakemcshane.shinyapps.io/mlmvmeta/


cat("Go to https://blakemcshane.shinyapps.io/mlmvmeta/\n")
cat("upload the files:\n")
cat("model1c.dat1.csv\n")
cat("model1c.dat2.csv\n")
cat("save the output as results1c.Rdata\n\n")
```


#### Model 5: Influence of AMAS and Maths test

```{r}
require(lme4)
dat <- read.csv("AllFischerData.csv", header=TRUE)

# Center and scale MathTest and AMAS to improve convergence:
dat$MathTest <- scale(dat$MathTest)
dat$AMAS <- scale(dat$AMAS)

# Prepare data for individual-level models:
dd <- melt(dat[,c("d250","d500","d750","d1000")])
dd$SubjectID <- rep(dat$Code, 4)
dd$LabID <- rep(dat$Lab, 4)
dd$FingerGroup <- rep(dat$FingerGroup, 4)
dd$Hand <- rep(dat$Hand, 4)
dd$ReadingDir <- rep(dat$ReadingDir, 4)
dd$MathTest <- rep(dat$MathTest, 4)
dd$AMAS <- rep(dat$AMAS, 4)
dd$varLabID <- paste(dd$variable, dd$LabID, sep="*")
dd$varSubjectID <- paste(dd$variable, dd$SubjectID, sep="*")

###################
# Fit lmer models #
###################

m2a <- lmer(value~variable*MathTest*AMAS-1-MathTest-AMAS-MathTest*AMAS + 
              (1|varLabID) + (MathTest*AMAS-1||LabID) + (1|SubjectID), data=dd)

VarCorr(m2a)

Estimates = summary(m2a)$coefficients %>% as.tibble() %>% add_column(Name = row.names(summary(m2a)$coefficients), .before = 1) 
Estimates$Lower = Estimates$Estimate - (qnorm(.975) * Estimates$`Std. Error`)
Estimates$Upper = Estimates$Estimate + (qnorm(.975) * Estimates$`Std. Error`)


Estimates$Name %>% stringr::str_replace_all(pattern = "variabled250", "250 ms ISI") %>%
  stringr::str_replace_all(pattern = "variabled500", "500 ms ISI") %>%
  stringr::str_replace_all(pattern = "variabled750", "750 ms ISI") %>%
  stringr::str_replace_all(pattern = "variabled1000", "1000 ms ISI") %>%
  stringr::str_replace_all(pattern = ":MathTest", " $\\\\times$ Maths test") %>%
  stringr::str_replace_all(pattern = ":AMAS", " $\\\\times$ AMAS") -> Estimates$Name 


m2a.n = dd$SubjectID %>% unique() %>% length()

Estimates %>% select(-Lower,-Upper) %>% rename(`$t$` = `t value`, `Std. Err.` = `Std. Error`) %>% 
  mutate(Estimate = round(Estimate,2), `Std. Err.` = round(`Std. Err.`,2), `$t$` = round(`$t$`,2)) -> Estimates
Estimates %>% add_column(`$n$` = m2a.n, .before = "Estimate") -> Estimates
RandomEffect  = summary(m2a)$varcor

model5.fe.stats = Estimates
save(list = "model5.fe.stats", file = "results5.Rdata")

model5 <- m2a
save(model5, file="results5.Rdata")


```
You can now run the script to produce the statistics at [make_statistics.R](helper_functions/make_statistics.R)
And you can run the script to produce the figures at [make_figures.R](helper_functions/make_figures.R)

All the .csv files should be moved to data/meta_data for later use
All the .Rdata files should be moved to data/processed_rdata for later use

Or run the code chunk below to do it automagically

```{r}
list.files(path = here::here(),pattern = "model[1-4,a-c]{1,2}.[dat12meta]{4}.csv", recursive = T, full.names = T) %>% map(function(x) file.copy(from = x, to = here::here("data/meta_data/",basename(x))))

list.files(path = here::here(),pattern = "results[1-5,a-d]{1,2}.Rdata", recursive = T, full.names = T) %>% map(function(x) file.copy(from = x, to = here::here("data/processed_rdata/",basename(x))))

```
